Optimizing httk's 3comp2 model

### 2025-05-27 data-raw/optimizing_httk_model.Rmd
Updated README.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
devtools::load_all()
library(httk)
```

@@

```{r}
load_dawson2021()
schems <- httk::get_cheminfo("dtxsid", species = "rat",
                             model = "3compartment2")[50:65] |>
  suppressWarnings()

@@

```{r}
test_pk <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  stat_model(model = c("model_flat", "model_1comp_cl_rest",
                       "model_1comp_cl_nonrest", "model_1comp_fup")) +
  settings_optimx(hessian = TRUE) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE)

test_fit <- do_fit(test_pk)
winmodel <- get_winning_model(test_fit)
View(winmodel)

pl <- plot(test_fit, use_scale_conc = TRUE, method = "bobyqa",best_fit = TRUE)
pl$final_plot[[1]]
pl$final_plot[[2]]
pl$final_plot[[3]]
pl$final_plot[[4]]

get_fit(test_fit) |> dplyr::filter(Chemical == "DTXSID4020458",
                                   param_name %in% c("Fup", "Clint"),
                                   model != "model_flat",
                                   convcode == 0) |>
  View()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
devtools::load_all()
library(dplyr)
library(httk)
```

@@

```{r}
load_dawson2021()
schems <- httk::get_cheminfo("dtxsid", species = "rat",
                             model = "3compartment2") |>
  suppressWarnings()

@@

```{r}
test_pk <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  stat_model(model = c("model_flat", "model_1comp_cl_rest",
                       "model_1comp_cl_nonrest", "model_1comp_fup")) +
  settings_optimx(hessian = TRUE) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE)

test_pk <- do_data_info(test_pk)
test_pk <- do_prefit(test_pk)
test_pk
gc()

test_pk$prefit$par_DF |> View()

test_fit <- do_fit(test_pk, n_cores = 8)
winmodel <- get_winning_model(test_fit)
View(winmodel)
winmodel %>% ungroup() %>% count(method, model)
get_fit(test_fit) %>%
  filter(convcode == 0) %>%
  ungroup() %>%
  distinct(Chemical, Species, model, method) %>% View()

pl <- plot(test_fit, use_scale_conc = TRUE,best_fit = FALSE, log10_C = TRUE,
           method = "bobyqa", fit_limits = 10)
pl %>%
  filter(Chemical == "DTXSID0020442") %>%
  pull(final_plot) %>% .[[1]]

pl %>%
  filter(Chemical == "DTXSID1022265") %>%
  pull(final_plot) %>% .[[1]]

get_fit(test_fit) %>%
  filter(Chemical == "DTXSID0020442", model == "model_1comp_cl_nonrest",
         param_name == "Clint", method == "L-BFGS-B") %>% View()
